\cvstatement{
	In Human–Computer Interaction, CHI and UIST are amongst the top-tier publication venues.
	Quick summary since 2012: Best Papers/Honorable Mention (4); UIST (13), CHI (9), TOCHI (1), MobileHCI (4), and other venues (9); Work done in UCLA (8), CMU (15), collaborated with Autodesk Research (5), Microsoft Research (2), Google Research (3), and Apple (1).
}

\cvitem{
	VRST '20
}{
	Yudai Tanaka, Arata Horie, \textbf{Xiang ‘Anthony’ Chen}. DualVib: Simulating Haptic Sensation of Dynamic Mass by Combining Pseudo-Force and Texture Feedback. \textit{Proc. ACM VRST 2020}. 
	Acceptance Rate: 26.5\%.
}

\cvitem{
	UIST '20
}{
	Jiahao Li, Jeeeun Kim, \textbf{Xiang ‘Anthony’ Chen}. Romeo: A Design Tool for Embedding Transformable Parts in 3D Models to Robotically Augment Default Functionalities. \textit{Proc. ACM UIST 2020}. 
	Acceptance Rate: 21\%.
}

\cvitem{
	UIST '20
}{
	Ritam Sarmah, Yunpeng Ding, Di Wang, Cheuk Yin Phipson Lee, Toby Jia-Jun Li, \textbf{Xiang ‘Anthony’ Chen}. Geno: A Developer Tool for Authoring Multimodal Interaction on Existing Web Applications. \textit{Proc. ACM UIST 2020}. 
	Acceptance Rate: 21\%.
}


\cvitem{
	CHI '20
}{
Yao Xie, Melody Chen, David Kao, Ge Gao, \textbf{Xiang `Anthony' Chen}. CheXplain: Enabling Physicians to Explore and Understand Data-Driven, AI-Enabled Medical Imaging Analysis. \textit{Proc. ACM CHI 2020}. Acceptance Rate: 24.3\%.
}

\cvitem{
	CHI '20
}{
Yuan Liang, Hsuan-Wei Fan, Zhujun Fang, Leiying Miao, Wen Li, Xuan Zhang, Weibin Sun, Kun Wang, Lei He, \textbf{Xiang `Anthony' Chen}. OralCam: Enabling Self-Examination and Awareness of Oral Health Using a Smartphone Camera. \textit{Proc. ACM CHI 2020}. Acceptance Rate: 24.3\%. \best{Best Paper Honorable Mention - top 5\%}
}

\cvitem{
	CACM '19
}{
Jennifer Mankoff, Megan Hofmann, \textbf{Xiang `Anthony' Chen}, Scott E. Hudson, Amy Hurst, Jeeeun Kim. Consumer-grade fabrication and its potential to revolutionize accessibility. \textit{Comm. ACM}, 62(10), October 2019.
}

\cvitem{
	SUI '19
}{
	Runchang Kang, Anhong Guo, Gierad Laput, Yang Li, \textbf{Xiang ‘Anthony’ Chen}. Minuet: Multimodal Interaction with an Internet of Things. \textit{Proc. ACM SUI 2019}. Acceptance Rate: 23\%.
}

\cvitem{
	UIST '19
}{
	Jiahao Li, Jeeeun Kim, \textbf{Xiang ‘Anthony’ Chen}. Robiot: A Design Tool for Actuating Everyday Objects with Automatically Generated 3D Printable Mechanisms. \textit{Proc. ACM UIST 2019}. 
		Acceptance Rate: 24\%.
}

\cvitem{
	IUI '19
}{
	Yao Xie, Ge Gao, \textbf{Xiang ‘Anthony’ Chen}. Outlining the Design Space of Explainable Intelligent Systems for Medical Diagnosis. CoRR abs/1902.06019 (2019).
}

\cvitem{
	UIST '18
}{
	Da-Yuan Huang, Teddy Seyed, Linjun Li, Zhihao Yao, Yuchen Jiao, \textbf{Xiang ‘Anthony’ Chen}, Xing-Dong Yang. Orecchio: Extending Body-Language through Actuated Static and Dynamic Auricular Postures. \textit{Proc. ACM UIST 2018}. Acceptance Rate: 21.3\%.
}

\cvitem{
	CHI '18
}{
	\textbf{Xiang ‘Anthony’ Chen}, Ye Tao, Guanyun Wang, Runchang Kang, Tovi Grossman, Stelian Coros, Scott Hudson. Forte: User-Driven Generative Design \textit{Proc. ACM CHI 2018}. Acceptance Rate: 25.7\%.
}

\cvitem{
	CHI '18
}{
	\textbf{Xiang ‘Anthony’ Chen}, Stelian Coros, Scott Hudson. Medley: A Library of Embeddables to Explore Rich Material Properties for 3D Printed Objects \textit{Proc. ACM CHI 2018}. Acceptance Rate: 25.7\%.
}

\cvitem{
	CHI '18\\
}{
	Jun Gong, Zheer Xu, Qifan Guo, Teddy Seyed, \textbf{Xiang ‘Anthony’ Chen}, Xiaojun Bi, Xing-Dong Yang. WrisText: One-handed Text Entry on Smartwatch using Wrist Gestures. \textit{Proc. ACM CHI 2018}. Acceptance Rate: 25.7\%. \best{Best Paper Honorable Mention - top 5\%}
}

\cvitem{
	CHI '18
}{ Byoungkwon An, Ye Tao, Jianzhe Gu, Tingyu Cheng, \textbf{Xiang ‘Anthony’ Chen}, Xiaoxiao Zhang, Wei Zhao, Youngwook Do, Shigeo Takahash, Hsiang-Yun Wu, Teng Zhang, Lining Yao. Thermorph: Democratizing 4D Printing of Self-Folding Materials and Interfaces \textit{Proc. ACM CHI 2018}. Acceptance Rate: 25.7\%.
}

\cvitem{
	CHI '17\\
%	C.20
}{
	Anhong Guo, Jeeeun Kim, \textbf{Xiang ‘Anthony’ Chen}, Tom Yeh, Scott Hudson, Jennifer Mankoff, Jeffrey Bigham. Façade: Auto-generating Tactile Interfaces to Appliances. \textit{Proc. ACM CHI 2017}, 5826-5838. Acceptance Rate: 25\%.
}

\cvitem{
	TOCHI '17\\
%    C.21
} {
	\textbf{Xiang ‘Anthony’ Chen}, Yang Li. Improv: An Input Framework for Improvising Cross-Device Interaction By Demonstration. \textit{ACM TOCHI}, 24(2), 15.
}

\cvitem{
	UIST '16\\
%    C.21
} {
	\textbf{Xiang ‘Anthony’ Chen}, Jeeeun Kim, Jennifer Mankoff, Tovi Grossman, Stelian Coros, Scott Hudson. Reprise: A Design Tool for Specifying, Generating, and Customizing 3D Printable Adaptations on Everyday Objects. \textit{Proc. ACM UIST 2016}, 29-39. Acceptance Rate: 20.6\%.
}

\cvitem{
	UIST '16\\
%	C.20
}{
	\textbf{Xiang ‘Anthony’ Chen}, Yang Li. Bootstrapping User-Defined Body Tapping Recognition with Offline-Learned Probabilistic Representation. \textit{Proc. ACM UIST 2016}, 359-364. Acceptance Rate: 20.6\%.
}

\cvitem{
	UIST '16\\
%	C.19
}{
	Anhong Guo, \textbf{Xiang ‘Anthony’ Chen}, Haoran Qi, Samuel White, Suman Ghosh, Chieko Asakawa, Jeffrey Bigham. VizLens: A Robust and Interactive Screen Reader for Interfaces in the Real World. \textit{Proc. ACM UIST 2016}, 651-664. Acceptance Rate: 20.6\%.
}

\cvitem{
	GI '16\\
%	C.18
}{
	Vikram Kamath Cannanure, \textbf{Xiang ‘Anthony’ Chen}, Jennifer Mankoff. Twist ‘n’ Knock: A One-handed Gesture for Smart Watches. \textit{Proc. GI 2016}, 189-193. Acceptance Rate: 39.4\%. 
}

\cvitem{
	CHI '16\\
%	C.17
}{
	Adrian de Freitas, Michael Nebeling, \textbf{Xiang ‘Anthony’ Chen}, Junrui Yang, Akshaye Shreenithi Kirupa Karthikeyan Ranithangam, Anind Dey. Snap-To-It: A User-Inspired Platform for Opportunistic Device Interactions. \textit{Proc. ACM CHI 2016}, 5909-5920. Acceptance Rate: 23.4\%.
}

\cvitem{
	IUI '16\\
%	C.16
}{
	Gierad Laput, \textbf{Xiang ‘Anthony’ Chen}, Chris Harrison. Sweepsense: Ad Hoc Configuration Sensing Using Reflected Swept-Frequency Ultrasonics. \textit{Proc. IUI 2016}, 332-335.
}

\cvitem{
	UIST '15\\
}{
	\textbf{Xiang ‘Anthony’ Chen}, Stelian Coros, Jennifer Mankoff, Scott Hudson. Encore: 3D Printed Augmentation of Everyday Objects with Printed-Over, Affixed and Interlocked Attachments. \textit{Proc. ACM UIST 2015}, 73-82. Acceptance Rate: 23.6\%.
}

\cvitem{
	UIST '15\\
}{
	Gierad Laput, \textbf{Xiang ‘Anthony’ Chen}, Chris Harrison. 3D Printed Hair: Fused Deposition Modeling of Soft Strands, Fibers, and Bristles. \textit{Proc. ACM UIST 2015}, 593-597. Acceptance Rate: 23.6\%.
}

\cvitem{
	MobileHCI '15
}{
	Tovi Grossman, \textbf{Xiang ‘Anthony’ Chen}, George Fitzmaurice. Typing on Glasses: Adapting Text Entry to Smart Eyewear. \textit{Proc. MobileHCI 2015}, 144-152. Acceptance Rate: 25.2\%.
}

\cvitem{
	UIST '14\\
%	\faTrophy
}{
	Ken Hinckley, Michel Pahud, Hrvoje Benko, Pourang Irani, Marcel Gavriliu, François Guimbretière, \textbf{Xiang 'Anthony' Chen}, Fabrice Matulic, William Buxton, Andrew Wilson. Sensing Techniques for Tablet+Stylus Interaction. \textit{Proc. ACM UIST 2014}, 605-614. Acceptance Rate: 22.2\%. \best{Best Paper Award - top 1\%}
}

\cvitem{
	UIST '14
}{
	\textbf{Xiang ‘Anthony’ Chen}, Julia Schwarz, Chris Harrison, Jennifer Mankoff, Scott Hudson. Air+Touch: Interweaving Touch \& In-Air Gestures. \textit{Proc. ACM UIST 2014}, 519-525. Acceptance Rate: 22.2\%.
}

\cvitem{
	UIST '14
}{
	\textbf{Xiang ‘Anthony’ Chen}, Tovi Grossman, George Fitzmaurice. Swipeboard: A Text Entry Technique for Ultra-Small Interfaces That Supports Novice to Expert Transitions. \textit{Proc. ACM UIST 2014}, 615-620. Acceptance Rate: 22.2\%.
}

\cvitem{
	UIST '14
}{
	Gierad Laput, Robert Xiao, \textbf{Xiang ‘Anthony’ Chen}, Scott Hudson, Chris Harrison. Skin Buttons: Cheap, Small, LowPowered and Clickable Fixed-Icon Laser Projectors. \textit{Proc. ACM UIST 2014}, 389-394. Acceptance Rate: 22.2\%.
}

\cvitem{
	CHI '14\\
}{
	\textbf{Xiang ‘Anthony’ Chen}, Tovi Grossman, Daniel Wigdor, George Fitzmaurice. Duet: Exploring Joint Interactions on a Smart Phone and a Smart Watch. Acceptance Rate: 22.8\%. \textit{Proc. ACM CHI 2014}, 159-168. \best{Best Paper Award - top 1\%}
}

\cvitem{
	MobileHCI '14
}{
	\textbf{Xiang ‘Anthony’ Chen}, Julia Schwarz, Chris Harrison, Jennifer Mankoff, Scott Hudson. Around-Body Interaction: Sensing \& Interaction Techniques for Proprioception-Enhanced Input with Mobile Devices. \textit{Proc. MobileHCI 2014}, 287-290. Acceptance Rate: 21.3\%.
}

\cvitem{
	Visual Computer '13
}{
	Bin Pan, Yong Zhao, Xiaoming Guo, \textbf{Xiang Chen}, Wei Chen, Qunsheng Peng. Perception-motivated visualization for 3D city scenes. \textit{The Visual Computer} 29.4 (2013): 277-286.
}


\cvitem{
	GI '12
}{
	Ken Hinckley, \textbf{Xiang ‘Anthony’ Chen}, Hrvoje Benko. Motion and Context Sensing Techniques for Pen Computing. \textit{Proc. GI 2012}, 71-78. Acceptance Rate: 33\%.
}


\cvitem{
	MobileHCI '12
}{
	\textbf{Xiang ‘Anthony’ Chen}, Nicolai Marquardt, Anthony Tang, Sebastian Boring, Saul Greenberg. Extending a Mobile Device’s Interaction Space through Body-Centric Interaction. \textit{Proc. MobileHCI 2012}, 151-160. Acceptance Rate: 25\%.
}

\cvitem{
	MobileHCI '12
}{
	Sebastian Boring, David Ledo, \textbf{Xiang ‘Anthony’ Chen}, Anthony Tang, Nicolai Marquardt, Saul Greenberg. The Fat Thumb: Using the Thumb's Contact Size for Single-Handed Mobile Interaction. \textit{Proc. MobileHCI 2012}, 39-48. Acceptance Rate: 25\%.
}

\cvitem{
	AVI '12
}{
	\textbf{Xiang ‘Anthony’ Chen}, Sebastian Boring, Sheelagh Carpendale, Anthony Tang, Saul Greenberg. Spalendar: Spatially Visualizing Group’s Calendar Activities as a Public Interactive Display. \textit{Proc. AVI 2012}, 689-696.
}

\cvitem{
	CAD/Graphics '11
}{
	Bin Pan, \textbf{Xiang Chen}, Xiaoming Guo, Wei Chen, Qunsheng Peng. Interactive Expressive Illustration of 3D City Scene. \textit{Proc. CAD/Graphics 2011}, 406-410.
}